Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-30 Talks/FU-Berlin/talk-part-1.tex
update of FU talk

\begin{frame}{Introduction} \large
Main challenge: \hfill No theorem provers for \emph{Higher-order Modal Logic} \\[1em]

Our idea: \hfill Exploit an embedding in \emph{Higher-order Classical Logic} \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

@@

\begin{itemize}
\item[A:] pen and paper: detailed natural deduction proof 
\item[B:] formalization: axioms, defs, thms  in \textsc{TPTP THF}
\item[C:] consistency: automatic verification with \textsc{Nitpick} 
\item[D:] proof automation: theorems provers Leo-II and \textsc{Satallax} 
\item[E:] step-by-step verification: proof assistant \textsc{Coq} 
\item[F:] automation \& verification: proof assistant 
  \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss later!}
\end{frame}

>>>>

\begin{frame}{Introduction} \large
Main challenge: \hfill No provers for \emph{Higher-order Modal Logic} \textcolor{red}{HML} \\[1em]

Our idea: \hfill Embedding in \emph{Higher-order Classical Logic} \textcolor{blue}{HOL} \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

@@

\begin{itemize}
\item[A:] pen and paper: detailed natural deduction proof 
\item[B:] formalization: axioms, defs, thms  in \textcolor{blue}{HOL}
\item[] proof automation: theorems provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] consistency: automatic verification with \textsc{Nitpick} 
\item[C:] step-by-step verification: proof assistant \textsc{Coq} 
\item[D:] automation \& verification: proof assistant 
  \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss later!}
\end{frame}
